---
title: "R+RStudio Tips and Tricks"
subtitle: "Hidden gems for improving workflow efficency"  
author: "Muhammad Aswan Syahputra"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE}
library(xaringanthemer)
solarized_dark(
  code_font_family = "Fira Code",
  code_font_url    = "https://cdn.rawgit.com/tonsky/FiraCode/1.204/distr/fira_code.css"
)
```

# Learn R in R
```
install.packages("swirl")
```
# For repetitive
```
install.packages("usethis")
```

# R tips and tricks
## Coding style
Write code in accordance to:
+ [Google's R style guide](https://google.github.io/styleguide/Rguide.xml), or
+ [The tidyverse style guide](https://style.tidyverse.org/)

## .Rprofile setup

## Saving and printing object


# RStudio hidden gems

## RStudio project

- Create new directory
- From existing directory
- From git

## Global options
+ Do not save and load .Rdata


## Layouts and theme
+ Console on right
+ Change theme
+ Use fonts with ligature

## The power of Tab
+ Autocompletion
+ File navigation

## Handy shortcut
+ `Ctrl + Enter` on highlighted example code at help page
+ `Ctrl + Shift + [number]`
+ `Ctrl + Up` at console
+ `Alt + Up/Down` at source editor
+ `Alt + Shift + Up/Down` at source editor
+ `Ctrl + Shift + F10`

## Addins 
+ `syler`
+ `datapasta`
+ `reprex`
+ `clipr`
+ `
